% !TEX root = ../thesis-sample.tex
\appendix
\chapter{I think you've let your personal feelings cloud your judgement.}
Now what are the possibilities of warp drive? Cmdr Riker's nervous system has been invaded by an unknown microorganism. The organisms fuse to the nerve, intertwining at the molecular level. That's why the transporter's biofilters couldn't extract it. The vertex waves show a K-complex corresponding to an REM state. The engineering section's critical. Destruction is imminent. Their robes contain ultritium, highly explosive, virtually undetectable by your transporter.

\section{We finished our first sensor sweep of the neutral zone.}
The easiest method.

\begin{equation}\label{eq:sum}
    x_k = \frac{a_k+b_k}{2}
\end{equation}

\section{False Position}
Exceeding reaction chamber thermal limit. We have begun power-supply calibration. Force fields have been established on all turbo lifts and crawlways. Computer, run a level-two diagnostic on warp-drive systems. Antimatter containment positive. Warp drive within normal parameters. I read an ion trail characteristic of a freighter escape pod. The bomb had a molecular-decay detonator. Detecting some unusual fluctuations in subspace frequencies.

\chapter{The game's not big enough unless it scares you a little.}\label{app:appendix_use}

This section might be referencing code and options that no longer exist in this version of the thesis class.
It should also be updated as well.

This appendix contains the portion of the users' manual that describes
how to use appendices with this template.  It is put in this appendix
rather than in Chapter~\cref{chap:intro} simply so that there are two
appendices.

\section{Starting the Appendices}
Actually, using appendices is quite simple.  Immediately after the end
of the last chapter and before the start of the first appendix, simply
enter the command \verb|\appendix|.  This will tell \LaTeX~to change
how it interprets the commands \verb|\chapter|, \verb|\section|,
\textit{etc.}

Each appendix is actually a chapter, so once the \verb|\appendix|
command has been called, start a new appendix by simply using the
\verb|\chapter| command.

Note that the \verb|\appendix| command should be called only
once--not before the start of each appendix.

All the fancy referencing and tools still work.
You only need to add the appendix command and all will be as it should be.

